Manuscript figures

### 2022-09-30 docs/manuscript_figures.Rmd
Figure5 for revision

quality_fig <- ggplot(
  tiles,
  aes(fill = factor(hardiness), x = score)) + 
  geom_bar(position = "stack") +
  scale_fill_brewer('Difficulty', palette = "Dark2") +
  xlab('Correctness') +
  ylab('Count') +
  theme_bw()

ggsave(here('docs/figures/humancheck_quality.png'),
       quality_fig,
       width = 4, height = 4, dpi = 300)
```

>>>>

quality_fig <- ggplot(
  tiles,
  aes(fill = factor(hardiness), x = score)) + 
  geom_bar(position = "stack") +
  scale_fill_brewer('Difficulty', palette = "Dark2") +
  xlab('Correctness') +
  ylab('Count') +
  theme_bw() +
    theme(text = element_text(size = 16))

# Figure 5, combination art
# Single figure (3.2 in in width), 1600 * 1600 at 500 dpi
ggsave(here('docs/figures/figure5_humancheck_quality.tiff'),
       quality_fig, bg = "white", units = "px", 
       width = 1600, height = 1600)
```
